Notation proposal

### 2011-06-02 results.tex
Added second box and whisker plot
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@831 ccdd05d5-56c1-461a-bf98-85f6876523b4

We expect two contributions to the \SNR\ loss to arise in our implementation of
the \lloid\ algorithm.  The first is the \SNR\ loss due to the truncation of
the SVD basis, which is fundamental, and estimates for it
exist~\cite{Cannon:2010p10398}.  The second comes from non ideal
implementations of resampling that cause signal loss.  We have measured the
effect of the resampling in the pipeline alone on a single waveform to gauge
the magnitude of the loss.  It is shown in figure \ref{fig:resamp_mm} as a
function of the quality of the {\tt audioresample} element (which is
proportional to the filter length used).  In both cases we have to compare the
\SNR\ loss to the expected \SNR\ loss that arises from the discreteness of the
template bank which is typically $\sim 3\%$.  We will consider a comparable
\SNR\ loss to be tolerable, but ideally would like to have a factor of 10 lower
loss from the \lloid\ implementation (i.e. no more than $\sim 0.3 \%$).  
%
\begin{figure}
\includegraphics{resamp_mm.pdf}
\caption{\label{fig:resamp_mm}Mis-match as a function of the {\tt
audioresample} element's filter length.  Increasing the filter length changes
the length of the sinc function filter that is used to decimate and interpolate
the data and filtered time series in our test pipeline.  Choosing a filter
length of 64 samples results in an acceptable loss of .2 \% in \SNR\ for the
chosen waveform.}
\end{figure}

\begin{figure}
	\label{fig:hist}
	\begin{center}
		\includegraphics{bw.pdf}
		\caption{Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse respones.  The \textsc{svd}
tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.
The whiskers denote the minimum and maximum mismatch over all templates.  The
diminishing improvement is caused by hitting the resampling match limit.}
	\end{center}
\end{figure}

>>>>

We expect two contributions to the \SNR\ loss to arise in our implementation of
the \lloid\ algorithm.  The first is the \SNR\ loss due to the truncation of
the SVD basis, which is fundamental, and estimates for it
exist~\cite{Cannon:2010p10398}.  The second comes from non ideal
implementations of resampling that cause signal loss.  We have measured the
effect of the resampling in the pipeline alone on a single waveform to gauge
the magnitude of the loss.  It is shown in figure \ref{fig:resamp_mm} as a
function of the quality of the {\tt audioresample} element (which is
proportional to the filter length used).  In both cases we have to compare the
\SNR\ loss to the expected \SNR\ loss that arises from the discreteness of the
template bank which is typically $\sim 3\%$.  We will consider a comparable
\SNR\ loss to be tolerable, but ideally would like to have a factor of 10 lower
loss from the \lloid\ implementation (i.e. no more than $\sim 0.3 \%$).  
%
\begin{figure}
	\label{fig:hist-interpolate}
	\begin{center}
		\includegraphics{bw_resample.pdf}
		\caption{Box-and-whisker plot of mismatch between nominal template bank and \lloid\ measured impulse respones.  The length $N^\shortuparrow$ of the interpolation filter is varied from 8 to 192.  The \textsc{svd} tolerance is kept fixed at $(1-10^{-6})$.  The lines in the center of the boxes denote the medians.  The upper and lower boundaries of the boxes show the upper and lower quartiles.  The whiskers denote the minimum and maximum mismatch over all templates.}
	\end{center}
\end{figure}

\begin{figure}
	\label{fig:hist-svd-tolerance}
	\begin{center}
		\includegraphics{bw.pdf}
		\caption{Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse respones.  The \textsc{svd}
tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.
The diminishing improvement is caused by hitting the resampling match limit.}
	\end{center}
\end{figure}
